%\paragraph{Title} Implementing Support for Reproducibility in a Restricted Access Environment: Case of the Federal Statistical Research Data Centers
\paragraph{Authors}  Lucia S Foster \email{lucia.s.foster@census.gov} (corresponding author), Shawn D Klimek \email{shawn.d.klimek@census.gov}, Danielle Sandler \email{danielle.h.sandler@census.gov}, Lars Vilhuber \email{lars.vilhuber@cornell.edu} (Cornell University)
\paragraph{One sentence description} This paper describes an effort at the U.S. Census Bureau to support reproducibility of research performed using confidential Census microdata.
\paragraph{Abstract} Replication of existing empirical work is one of the cornerstones of robust scientific inquiry. This paper describes an effort at the U.S. Census Bureau to support reproducibility of research performed using confidential Census microdata. This effort has three major components: documentation, access, and dissemination. The output from projects using Census microdata is already controlled and documented for disclosure avoidance reasons. We will leverage this existing structure to provide better tools for researchers using Census data to document the data and code they use for their research papers. As part of this additional documentation, we will clarify and improve the process by which their data and code can be accessed for replication purposes. The Federal Statistical Research Data Center (FSRDC) system provides access to Census microdata to an increasing number of researchers across the country. We plan to provide access to researchers who wish to conduct replications through a shorter and simpler process than the typical FSRDC research project proposal. We plan to disseminate the results of the replication studies, regardless of the outcome of those studies, as an ongoing CES Replication Studies series. This will add transparency to the process, increase the exposure of these studies, and reduce the effects publication bias. The goal of this project is to improve the understanding of the U.S. economy by making the research conducted by Census internal researchers and in the FSRDCs robust and replicable by the research community.

\paragraph{Keywords} Reproducibility; Confidential Data.